Sparse Function-space Representation \\ of Neural Networks

### 2023-05-11 paper/main.tex
started new related work section

\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model. If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citet{rasmussen2006gaussian} for details. We linearise the neural network function

% The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}. Central to the approximation is how to form the hessian of \cref{eq-empirical-risk} a common approach is to use the the GGN approximation which would result in the following posterior $q(\vw;\vw^*, \MSigma_{\textrm{GGN}})$ where

As was pointed out in \citep{immerScalable2021} we can view the approximation in two steps.

Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
The GP prior is then given by,
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
  % \mu_{\weights_{i}^{*}}(\cdot)
  \mu(\cdot)
  = 0 \quad
  % = f(\cdot ;\weights^{*}) \quad
  % K_{\weights_{i}^{*}}(\cdot, \cdot')
  k(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\gamma^{2}} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{align}
where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
\todo{what mean function shoudl this use???}
\todo{NTK times some factor??}
with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$
%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
% \citep{immerImprovingPredictionsBayesian2021}
% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.

>>>>

\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model. If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details. We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ giving thus our GP prior becomes:
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
  % \mu_{\weights_{i}^{*}}(\cdot)
  \mu(\cdot)
  = 0 \quad
  % = f(\cdot ;\weights^{*}) \quad
  % K_{\weights_{i}^{*}}(\cdot, \cdot')
  k(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\gamma^{2}} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{align}
where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}$
